aids

### 2023-04-05 analyses/optimAids.Rmd
File Changes

---
title: "support"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 10
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

```{r}

library(reticulate)
```

@@

```{r setup, include=T}
set.seed(1234)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0# 10^-7

@@

baselineTrials<-5

@@

```{r supPrep,eval=T}

source_python('src/getSUP.py')
data<- as.data.frame(do.call(cbind, getSupportPycox()))

colnames(data)[ncol(data)-1]<-'time'
colnames(data)[ncol(data)]<-'status'

data<-data[-which(data$x2 %in% c(8,9)),]

for(i in c(2,3,4,5,6,7)){#3,4,
  data[, i]<-as.factor(data[, i])
}
data<-as.data.frame(model.matrix(~.,data)[,-1])
#data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))

covs<-colnames(data)
names(data)[seq(1,length(covs)-2)] <- paste("z", seq(1,length(covs)-2), sep="")

names(data)[ncol(data)-1]<-"time"
names(data)[ncol(data)]<-"status"

covs<-colnames(data)

#toDiv<-max(data$time)
#data$time<-data$time/toDiv
#data$time<-data$time/max(data$time)
spec = c(train = .85, test = .15)

@@

res = split(data, g)
saveRDS(res$test,"supportTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"supportCV.rds")

@@

klist<-readRDS("supportCV.rds")

lr=c(0.001)
drpt=c(0.25,0.5)
layer1=c(10,20,30)
layer2=c(10,20,30)
bsize=c(floor(nrow(klist[[1]]$train)/100))
actv=c("relu","linear")#,"tanh"
alp=c(0)

@@

```{r hyperOpDsurv,eval=reoptimize}

optimDeepSurv<-function(klist,test,times,baselineTrials,lr,drpt,layer1,layer2,bsize,actv){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             bsize=c(bsize),
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=paramTrials[i,]$bsize
      actv=paramTrials[i,]$actv
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/optimDSurv.py')

      currentTime<-Sys.time() 
      coxnnsurv=fitDeepSurv(train,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
      #tempVal<-append(tempVal,min(coxnnsurv$val_metrics$scores$loss$score))
      scores<-na.omit(coxnnsurv$val_metrics$scores$loss$score)

      tempVal<-append(tempVal,scores[length(scores)])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      # coxnnsurv<-coxnnsurv[[1]]
      # coxnnsurv<-t(coxnnsurv)
      # #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
      # cnnCleaned<-pyProcess(coxnnsurv,times=times)
      # colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
      # py_run_string("del fitDeepSurv")
      rm(fitDeepSurv)
      # brierFinalResults <- Score(list('ds'=cnnCleaned),
      #                            data =as.data.frame(val),#rbind(train,val) 
      #                            formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
      #                            se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score
      # cutted<-brierFinalResults[which(brierFinalResults$model=="ds"),]
      #tempRes<-append(tempRes,mean(cutted[-c(1,2,24,25)]$IPA))
    }

@@

klist<-readRDS("supportCV.rds")
test<-readRDS("supportTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

bestDS<-optimDeepSurv(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,bsize,actv)

@@

optimDeepHit<-function(klist,test,times,baselineTrials,lr,drpt,layer1,layer2,bsize,actv,alp){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             bsize=c(bsize),
                                             actv=actv,
                                             alp=alp,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=paramTrials[i,]$bsize
      actv=paramTrials[i,]$actv
      alp=paramTrials[i,]$alp
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/optimDH.py')

      currentTime<-Sys.time() 
      hitnnSurv=fitDeephit(train,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
      #tempVal<-append(tempVal,min(hitnnSurv$val_metrics$scores$loss$score))
      scores<-na.omit(hitnnSurv$val_metrics$scores$loss$score)

      tempVal<-append(tempVal,scores[length(scores)])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }
    rm(fitDeephit)

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(mean(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("supportCV.rds")
test<-readRDS("supportTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

bestDH<-optimDeepHit(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,bsize,actv,alp)

@@

      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds,1)

      #train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds,1)
      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])
      ),
      as.matrix(valcb[,ncol(valcb)-1,drop=F])
      )
      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))
      #val[[1]][[2]]<-rep(0,nrow(val[[1]][[1]]))

@@

      fit<-fitSmoothHaz(cbnn,
                        epochs=epo,
                        batch_size=bsize,
                        verbose=0,
                        monitor="val_loss",
                        #val_split=0.2,
                        min_delta=min_delta,
                        patience=patience,val=val)
      #tempVal<-append(tempVal,min(fit$resultOfFit$metrics$val_loss))

      scores<-na.omit(fit$resultOfFit$metrics$val_loss)

      tempVal<-append(tempVal,scores[length(scores)])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      rm(cbnn,fit,covars_input,covars_output)
    }
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("supportCV.rds")
test<-readRDS("supportTest.rds")

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,bsize,actv)
#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]
```

@@

saveRDS(winners,"supportWins.rds")

@@

winners<-readRDS("supportWins.rds")

klist<-readRDS("supportCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("supportTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 22
  )

@@

  lr=winners$ds$lr
  drpt=winners$ds$drpt
  layer1=winners$ds$layer1
  layer2=winners$ds$layer2
  bsize=winners$ds$bsize
  actv=winners$ds$actv

  source_python('src/dsurv.py')
  coxnnsurv=fitDeepSurv(train,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
  coxnnsurv<-t(coxnnsurv)
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

    miniee <- Score(list('mod'=cnnCleaned),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score
   miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))]

  #############################
  ###DEEPHIT
  #############################
  lr=winners$dh$lr
  drpt=winners$dh$drpt
  layer1=winners$dh$layer1
  layer2=winners$dh$layer2
  bsize=winners$dh$bsize
  actv=winners$dh$actv
  alp=winners$dh$alp
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
  hitnnSurv<-t(hitnnSurv)
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-times
  py_run_string("del fitDeephit")
  rm(fitDeephit)

@@

  val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))   
  lr=winners$cbnn$lr
  drpt=winners$cbnn$drpt
  layer1=winners$cbnn$layer1
  layer2=winners$cbnn$layer2
  bsize=c(floor(nrow(train)/winners$cbnn$nBatch))
  actv=winners$cbnn$actv
   # 
   # 
   #  lr=0.001
   #  drpt=0.5
   #  layer1=10
   #  layer2=10
   #  patience=10
    actv='linear'

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100supportBrier.rds')
  saveRDS(cScore,'results/100supportcidx.rds')
  pos=pos+1

@@

```{r plotsupport}

BrierIPAList<-readRDS('results/100supportBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.2))
#end_time-start_time

>>>>

---
title: "aids"
output: html_document
params:
  epo: 200
  patience: 5
  iteration: 2
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

```{r}
library(reticulate)

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_aids<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

#baselineTrials<-2

@@

```{r aidsPrep,eval=T}

library(MASS)
aids<-Aids2

aids<-aids[which(aids$T.categ=="hs"),]
aids<-aids[which(aids$sex=="M"),]

stattt<-as.factor(aids$status)

levels(stattt)<-c(0,1)
preData<-data.frame(#sex=as.factor(aids$sex),
                    #tcat=as.factor(aids$T.categ),
                    age=as.numeric(aids$age),
                    time=as.numeric(as.numeric(aids$death)-as.numeric(aids$diag)),
                    status=as.numeric(stattt)-1
)
preData<-na.omit(preData)

modData<-as.data.frame(model.matrix(~.,preData)[,-1])

data<-as.data.frame(apply(modData,2,as.numeric))

spec = c(train = .85, test = .15)

@@

saveRDS(res$test,"aidsTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"aidsCV.rds")

@@

klist<-readRDS("aidsCV.rds")

# lr=c(0.001)
# drpt=c(0.25,0.5)
# layer1=c(10,20,30)
# layer2=c(10,20,30)
# bsize=c(floor(nrow(klist[[1]]$train)/100))
# actv=c("relu","linear")#,"tanh"
# alp=c(0)

lr=c(0.001,0.0005)
drpt=c(0.25,0.1)
layer1=c(20,50,100)
layer2=c(10,25,50)
nBatch=c(100,500,1000)
actv=c("relu","linear","tanh")#
alp=c(0,0.5,1)

lr=c(0.001)
drpt=c(0.25)
layer1=c(20)
layer2=c(10)
nBatch=c(1000,100)
actv=c("relu")#
alp=c(0)

@@

```{r hyperOpDsurv}

optimDeepSurv<-function(klist,test,baselineTrials,lr,drpt,layer1,layer2,nBatch,actv){

@@

    for(data in klist){
      currentTime<-Sys.time() 
      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=ceiling(nrow(train)/paramTrials[i,]$nBatch)
      actv=paramTrials[i,]$actv
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/dsurv.py')

      ctrain<-train
      #ctrain$time<- train$time + runif(nrow(train),-0.000001,0.000001)

      coxnnsurv=fitDeepSurv(ctrain,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)

      coxnnsurv<-t(coxnnsurv)
      cnnCleaned<-pyProcess(coxnnsurv,times=times)
      colnames(cnnCleaned)<-times
      py_run_string("del fitDeepSurv")
      rm(fitDeepSurv)

      miniee <- Score(list('mod'=cnnCleaned),
                      data =val, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      # coxnnsurv<-coxnnsurv[[1]]
      # coxnnsurv<-t(coxnnsurv)
      # #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
      # cnnCleaned<-pyProcess(coxnnsurv,times=times)
      # colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
      # py_run_string("del fitDeepSurv")
      # rm(fitDeepSurv)
      # brierFinalResults <- Score(list('ds'=cnnCleaned),
      #                            data =as.data.frame(val),#rbind(train,val) 
      #                            formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
      #                            se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score
      # cutted<-brierFinalResults[which(brierFinalResults$model=="ds"),]
      #tempRes<-append(tempRes,mean(cutted[-c(1,2,24,25)]$IPA))
    }

@@

klist<-readRDS("aidsCV.rds")
test<-readRDS("aidsTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

optimDeepHit<-function(klist,test,times,baselineTrials,lr,drpt,layer1,layer2,nBatch,actv,alp){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             nBatch=nBatch,
                                             actv=actv,
                                             alp=alp,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

@@

    for(data in klist){
      currentTime<-Sys.time() 
      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=ceiling(nrow(train)/paramTrials[i,]$nBatch)
      actv=paramTrials[i,]$actv
      alp=paramTrials[i,]$alp
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/deephitter.py')
      hitnnSurv=fitDeephit(train,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
      hitnnSurv<-t(hitnnSurv)
      deephitCleaned<-pyProcess(hitnnSurv,times=times)
      colnames(deephitCleaned)<-times
      py_run_string("del fitDeephit")
      rm(fitDeephit)

      miniee <- Score(list('mod'=deephitCleaned),
                      data =val, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }

klist<-readRDS("aidsCV.rds")
test<-readRDS("aidsTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

bestDH<-optimDeepHit(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds,maxTime)

      #train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds,maxTime)
      valTest<-val
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])
      ),
      as.matrix(valcb[,ncol(valcb)-1,drop=F])
      )
      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))
      #val[[1]][[2]]<-rep(0,nrow(val[[1]][[1]]))

@@

      fit<-fitSmoothHaz(cbnn,
                        epochs=epo,
                        batch_size=bsize,
                        verbose=0,
                        monitor="val_loss",
                        #val_split=0.2,
                        min_delta=min_delta,
                        patience=patience,val=val)
      #tempVal<-append(tempVal,min(fit$resultOfFit$metrics$val_loss))
      annPreds<-aar(fit,
                    times=times,
                    x_test=valTest[,-c(ncol(valTest))]
      )

      miniee <- Score(list('mod'=annProperpoly),
                      data =valTest, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])

      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      rm(cbnn,fit,covars_input,covars_output)
    }

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("aidsCV.rds")
test<-readRDS("aidsTest.rds")

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,nBatch,actv)
#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]
```

@@

saveRDS(winners,"aidsWins.rds")

@@

winners<-readRDS("aidsWins.rds")

klist<-readRDS("aidsCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("aidsTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 20
  )

@@

  lr=winners$ds$lr
  drpt=winners$ds$drpt
  layer1=winners$ds$layer1
  layer2=winners$ds$layer2
  bsize=ceiling(nrow(train)/winners$ds$nBatch)
  actv=winners$ds$actv

  source_python('src/dsurv.py')
  ctrain<-train
  ctrain$time<- train$time

  coxnnsurv=fitDeepSurv(ctrain,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
  coxnnsurv<-t(coxnnsurv)

  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  #############################
  ###DEEPHIT
  #############################
  lr=winners$dh$lr
  drpt=winners$dh$drpt
  layer1=winners$dh$layer1
  layer2=winners$dh$layer2
  bsize=ceiling(nrow(train)/winners$dh$nBatch)
  actv=winners$dh$actv
  alp=winners$dh$alp
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
  hitnnSurv<-t(hitnnSurv)
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-times
  py_run_string("del fitDeephit")
  rm(fitDeephit)

@@

  val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))   
  lr=winners$cbnn$lr
  drpt=winners$cbnn$drpt
  layer1=winners$cbnn$layer1
  layer2=winners$cbnn$layer2
  bsize=c(floor(nrow(train)/winners$cbnn$nBatch))
  actv=winners$cbnn$actv
  # 
  # 
  #  lr=0.001
  #  drpt=0.5
  #  layer1=10
  #  layer2=10
  #  patience=10
  #actv='linear'

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100aidsBrier.rds')
  saveRDS(cScore,'results/100aidscidx.rds')
  pos=pos+1

@@

```{r plotaids}

BrierIPAList<-readRDS('results/100aidsBrier.rds')

@@

ipa+coord_cartesian(ylim=c(-0.1,0.5))
#end_time-start_time
